---
title: "Final Client Package"
subtitle: " Sino Yoga Proposal Presentation"
author: "Stephanie Gutierrez, Marlen Garcia, Erika Barajas, Abby Ortiz"
institute: "IBM 6530 Cal Poly Pomona"
date: "`r Sys.Date()`"
format: 
  revealjs:
    theme: serif
    width: 1600
    height: 900
    footer: Sino Yoga
    transition: slide
    transition-speed: default
    incremental: false
    toc: true
    toc-depth: 1
    slide-number: true
    scrollable: true
    smaller: true
    code-fold: false
    code-overflow: wrap
    number-sections: false
    number-depth: 5
    embed-resources: true
    css: styles.css
editor: visual
execute: 
  echo: true
  freeze: auto
---

## Deliverable 1

### Big Query Source

### KPI Logic & Controls

### Definitions & Caveats

### Stakeholder Layout

#### Stakeholder Q1

> How do we increase visibility and attract high-intent users?

```{r}
#| echo: false
library(tidyverse)
library(gt)

kpi_table <- tibble(
  KPIs = c("Impressions", "Click-Through Rate (CTR)"),
  `Metric Definition` = c("Impressions: number of times a video thumbnail is shown to users on YouTube, measures how often content is seen reach and visibility of videos",
    "CTR = (Clicks / Impressions x 100) Measuring how effectively titles/thumbnails drive clicks on videos"
  ),
  `Break Down` = c("Traffic Source (Search, Browse, Suggested", "Video Title /Keyword & UTM"),
  `Data Source` = c("YouTube Studio Analytics", "GA4 & GTM"),
  Assumptions = c(
    "Search Traffic= high intent users", "CTR reflects content packaging effectiveness"
  )
)

kpi_table |>
  gt() |>
  tab_header(
    title = "Stakeholder Layout",
    subtitle = "Q1"
  ) |>
  cols_label(
    KPIs = "KPI",
    `Metric Definition` = "Metric Definition",
    `Break Down` = "Breakdown",
    `Data Source` = "Data Source",
    Assumptions = "Assumptions"
  ) |>
  tab_options(
    table.font.size = 13,
    heading.title.font.size = 16,
    heading.subtitle.font.size = 13,
    table.width = pct(100)
  )
```

#### STAKEHOLDER Q2

> How can we build a cohesive yoga community that connects viewers across YouTube, our website to drive engagement and long-term growth?

```{r}
#| echo: false
library(tidyverse)
library(gt)

kpi_table <- tibble(
  KPIs = c("Cross Platform Traffic (YouTube -> Website)", "Engagement Rate", "Returning Users"),
  `Metric Definition` = c("Number of website sessions from YouTube", " Percentage of users who interact with content (likes, comments, & shares E= (total interactions/total views) x100","Percentage of users who return to the website or channel after first visit Returning Users Rate =(Returning users / Total Users) x100"
  ),
  `Break Down` = c("Traffic Source & UTM Parameters", "Device & Content Type","Geography" ),
  `Data Source` = c("YouTube Studio Analytics", "GA4", "GTM"),
  Assumptions = c(
    "YouTube users represent core audience", "Engagement reflect active viewers", "Returning users indicate stronger community engagement"
  )
)

kpi_table |>
  gt() |>
  tab_header(
    title = "Stakeholder Layout",
    subtitle = "Q2"
  ) |>
  cols_label(
    KPIs = "KPI",
    `Metric Definition` = "Metric Definition",
    `Break Down` = "Breakdown",
    `Data Source` = "Data Source",
    Assumptions = "Assumptions"
  ) |>
  tab_options(
    table.font.size = 13,
    heading.title.font.size = 16,
    heading.subtitle.font.size = 13,
    table.width = pct(100)
  )
```

#### STAKEHOLDER Q3

> How can we deepen engagement with our YouTube viewers and build enough value and trust for them to choose a paid membership?

```{r}
#| echo: false
library(tidyverse)
library(gt)

kpi_table <- tibble(
  KPIs = c("Watch Time", "Average View Duration", "Engagement Rate", "Conversion Rate"),
  `Metric Definition` = c("Total time viewers watch videos(hrs) indicates depth of engagement & content value", "Average time viewer spends watching video (AVD= Watch Time / Views)","Percentage of users who interact with content (likes, comments, & shares E= (total interactions/total views) x100", "Percentage of engaged users who purchase a membership ((# memberships / users) x 100"
  ),
  `Break Down` = c("video type & content type", "video length & audience segment", "video topic &  CTA","Traffic Source & User Journey Stage"),
  `Data Source` = c("YouTube Studio Analytics", "YouTube Studio Analytics", "YouTube Studio Analytics", "GA4 & GTM"),
  Assumptions = c(
    "Higher watch time indicate strong value & trust","engagement reflects active users with channel", "users who engage & return frequently are more likely to convert to paying members", "conversion tracking requires integration of mulitple platforms"
  )
)


kpi_table |>
  gt() |>
  tab_header(
    title = "Stakeholder Layout",
    subtitle = "Q3"
  ) |>
  cols_label(
    KPIs = "KPI",
    `Metric Definition` = "Metric Definition",
    `Break Down` = "Breakdown",
    `Data Source` = "Data Source",
    Assumptions = "Assumptions"
  ) |>
  tab_options(
    table.font.size = 13,
    heading.title.font.size = 16,
    heading.subtitle.font.size = 13,
    table.width = pct(100)
  )
```

## Business Problem

Sino Yoga lacks a structured, data-driven digital growth strategy — limiting visibility, engagement, and revenue.

-   **Visibility**: Low YouTube search presence; content not optimized for discovery

-   **Engagement**: High reach, low interaction and retention

-   **Monetization**: Audience interest not converting to revenue; no clear funnel

-   **Integration**: Platforms operate independently, not as a connected funnel

## Deliverable 3

testing
